---
title: "Anime Data Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

[Source](https://www.kaggle.com/datasets/andreuvallhernndez/myanimelist)

```{r, message=FALSE}
library(tidymodels)
library(patchwork)

anime_raw <- read_csv("data/anime.csv")
manga_raw <- read_csv("data/manga.csv")
```

# Ideas

Interesting

- Ratings of animes over time
- Predict genre using NLP
- broadcast_time / broadcast_day vs. score
- Connect anime + manga
- Use related animes to predict new ones (usually a good indicator)
- Incorporate number of members/favorites before
- Maybe add tiers for producers
- Account for missing / incorrect parameters in the mean score function
- Remove title in recipe instead

Broad Goals

- Finish all the models
- Rshiny App
- Find a way to access to MAL API

**Goal:** predict anime scores

**Remove:** anime_id (adds nothing), title (adds nothing), start_date (can use start season), end_date (doesn't really matter), total_duration (avg times number of episodes - nvm doesn't really matter), approved (?), created_at (adds nothing), updated_at (adds nothing), real_start_date (can use start season), real_end_date (doesn't really matter), synopsis (not doing NLP), background (doesn't matter), main_picture (doesn't matter), url (doesn't matter), trailer_url (doesn't matter), title_english (doesn't matter), title_japanese (doesn't matter), title_symptoms (doesn't matter), sfw (use rating instead), episode_duration (largely taken care of by genre), licensors (may not be available at times), broadcast_time (too hard), broadcast_day (lot of missing values), start_year (doesn't make sense for next few years)

Keep: score, type, episodes, source, members, favorites, rating, genres, themes, demographics, studios, producers

# Exploratory Data Analysis {.tabset}

```{r}
anime <- anime_raw %>%
  # filter out any animes that do not have scores
  drop_na(score) %>%
  # keep only animes that have finished airing (since scores tend to fluctuate during the season)
  filter(status == "finished_airing") %>%
  # select relevant variables (title is not a predictor but is kept here for visualization purposes)
  select(title, score, type, episodes, source, members, favorites, rating, 
         genres, themes, demographics, studios, producers) %>%
  # filter out rows that have NA values
  drop_na()
```

## Scores

```{r}
p1 <- anime %>%
  ggplot(aes(x = score)) +
  geom_histogram() +
  labs(title = "Histogram of Scores")

p2 <- anime %>%
  ggplot(aes(x = score)) +
  geom_boxplot(outlier.color = "red") +
  labs(title = "Boxplot of Scores")

p1 + p2 + plot_layout(ncol = 1)
```

## Type

```{r}
anime %>%
  group_by(type) %>%
  summarise(score = mean(score)) %>%
  
  arrange(desc(score)) %>%
  mutate(type = fct_inorder(type)) %>%
  
  ggplot(aes(x = type, y = score)) +
  geom_bar(stat = "identity")
```

## Episodes

```{r}
library(ggrepel)
anime %>%
  ggplot(aes(x = episodes, y = score)) +
  geom_point() +
  geom_text_repel(data = subset(anime, episodes > 550),
                  aes(label = title),
                  box.padding = 1)
```

## Source

```{r}
anime %>%
  group_by(source) %>%
  summarise(score = mean(score)) %>%
  
  arrange(desc(score)) %>%
  mutate(source = fct_inorder(source)) %>%
  
  ggplot(aes(x = source, y = score)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90))
```

## Members

```{r}
anime %>%
  ggplot(aes(x = members, y = score)) +
  geom_point() +
  geom_text_repel(data = subset(anime, members > 2.7e6),
                  aes(label = title),
                  box.padding = 0.7)
```

## Favorites

```{r}
anime %>%
  ggplot(aes(x = favorites, y = score)) +
  geom_point() +
  geom_text_repel(data = subset(anime, favorites > 1.5e5),
                  aes(label = title),
                  box.padding = 0.5)
```

## Rating

```{r}
anime %>%
  group_by(rating) %>%
  summarise(score = mean(score)) %>%
  
  arrange(desc(score)) %>%
  mutate(rating = fct_inorder(rating)) %>%
  
  ggplot(aes(x = rating, y = score)) +
  geom_bar(stat = "identity")
```

## Genres

```{r}
# helper function
replace_empty_string <- function(.str) {
  ifelse(.str == "", "Other or NA", .str)
}
```

taken from [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-04-23)

```{r}
anime %>%
  mutate(genres = str_remove(genres, "\\["),
         genres = str_remove(genres, "\\]")) %>% 
  separate_rows(genres, sep = ",") %>% 
  mutate(genres = str_remove(genres, "\\'"),
         genres = str_remove(genres, "\\'"),
         genres = str_trim(genres)) %>%
  mutate_at("genres", ~ replace_empty_string(.x)) %>%
  group_by(genres) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))
```

```{r}
anime %>%
  mutate(genres = str_remove(genres, "\\["),
         genres = str_remove(genres, "\\]")) %>% 
  separate_rows(genres, sep = ",") %>% 
  mutate(genres = str_remove(genres, "\\'"),
         genres = str_remove(genres, "\\'"),
         genres = str_trim(genres)) %>%
  mutate_at("genres", ~ replace_empty_string(.x)) %>%
  ggplot(aes(x = genres, y = score, color = genres)) +
  geom_boxplot() +
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")
```

## Themes

```{r}
anime %>%
  mutate(themes = str_remove(themes, "\\["),
         themes = str_remove(themes, "\\]")) %>% 
  separate_rows(themes, sep = ",") %>% 
  mutate(themes = str_remove(themes, "\\'"),
         themes = str_remove(themes, "\\'"),
         themes = str_trim(themes)) %>%
  mutate_at("themes", ~ replace_empty_string(.x)) %>%
  group_by(themes) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))
```

## Demographics

```{r}
anime %>%
  mutate(demographics = str_remove(demographics, "\\["),
         demographics = str_remove(demographics, "\\]")) %>% 
  separate_rows(demographics, sep = ",") %>% 
  mutate(demographics = str_remove(demographics, "\\'"),
         demographics = str_remove(demographics, "\\'"),
         demographics = str_trim(demographics)) %>%
  mutate_at("demographics", ~ replace_empty_string(.x)) %>%
  group_by(demographics) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))
```

## Studios

```{r}
anime %>%
  mutate(studios = str_remove(studios, "\\["),
         studios = str_remove(studios, "\\]")) %>% 
  separate_rows(studios, sep = ",") %>% 
  mutate(studios = str_remove(studios, "\\'"),
         studios = str_remove(studios, "\\'"),
         studios = str_trim(studios)) %>%
  mutate_at("studios", ~ replace_empty_string(.x)) %>%
  group_by(studios) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))
```

## Producers

```{r}
anime %>%
  mutate(producers = str_remove(producers, "\\["),
         producers = str_remove(producers, "\\]")) %>% 
  separate_rows(producers, sep = ",") %>% 
  mutate(producers = str_remove(producers, "\\'"),
         producers = str_remove(producers, "\\'"),
         producers = str_trim(producers)) %>%
  mutate_at("producers", ~ replace_empty_string(.x)) %>%
  group_by(producers) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))
```

# More Cleaning {.tabset}

## Genres

```{r}
genres_mean_scores <- anime %>%
  mutate(genres = str_remove(genres, "\\["),
         genres = str_remove(genres, "\\]")) %>% 
  separate_rows(genres, sep = ",") %>% 
  mutate(genres = str_remove(genres, "\\'"),
         genres = str_remove(genres, "\\'"),
         genres = str_trim(genres)) %>%
  mutate_at("genres", ~ replace_empty_string(.x)) %>%
  group_by(genres) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))

genres_mean_scores
```

## Themes

```{r}
themes_mean_scores <- anime %>%
  mutate(themes = str_remove(themes, "\\["),
         themes = str_remove(themes, "\\]")) %>% 
  separate_rows(themes, sep = ",") %>% 
  mutate(themes = str_remove(themes, "\\'"),
         themes = str_remove(themes, "\\'"),
         themes = str_trim(themes)) %>%
  mutate_at("themes", ~ replace_empty_string(.x)) %>%
  group_by(themes) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))

themes_mean_scores
```

## Studios

```{r}
studios_mean_scores <- anime %>%
  mutate(studios = str_remove(studios, "\\["),
         studios = str_remove(studios, "\\]")) %>% 
  separate_rows(studios, sep = ",") %>% 
  mutate(studios = str_remove(studios, "\\'"),
         studios = str_remove(studios, "\\'"),
         studios = str_trim(studios)) %>%
  mutate_at("studios", ~ replace_empty_string(.x)) %>%
  group_by(studios) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))

studios_mean_scores
```

## Demographics

```{r}
demographics_mean_scores <- anime %>%
  mutate(demographics = str_remove(demographics, "\\["),
         demographics = str_remove(demographics, "\\]")) %>% 
  separate_rows(demographics, sep = ",") %>% 
  mutate(demographics = str_remove(demographics, "\\'"),
         demographics = str_remove(demographics, "\\'"),
         demographics = str_trim(demographics)) %>%
  mutate_at("demographics", ~ replace_empty_string(.x)) %>%
  group_by(demographics) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))

demographics_mean_scores
```

## Producers

```{r}
producers_mean_scores <- anime %>%
  mutate(producers = str_remove(producers, "\\["),
         producers = str_remove(producers, "\\]")) %>% 
  separate_rows(producers, sep = ",") %>% 
  mutate(producers = str_remove(producers, "\\'"),
         producers = str_remove(producers, "\\'"),
         producers = str_trim(producers)) %>%
  mutate_at("producers", ~ replace_empty_string(.x)) %>%
  group_by(producers) %>%
  summarise(score = mean(score)) %>%
  arrange(desc(score))

producers_mean_scores
```

# Calculate Scores

```{r}
total_mean_score <- anime %>% 
  pull(score) %>% 
  mean()

# categories = ['category1', 'category2']
category_mean_score <- function(categories, df_map, replace_empty = total_mean_score) {
  # get mapped values
  category <- df_map %>% pull(1)
  score <- df_map %>% pull(2)
  
  # use mean score over all animes if input is empty
  if (categories == "[]") {
    return (replace_empty)
  }
  
  # otherwise, calculate the mean score over those categories
  else {
    mean_score <- categories %>%
      str_remove("\\[") %>%
      str_remove("\\]") %>%
      str_remove_all("\\'") %>%
      
      strsplit(split = ", ") %>%
      unlist() %>%
      plyr::mapvalues(from = category, 
                      to = score,
                      warn_missing = FALSE) %>%
      as.numeric() %>%
      mean()
    
    return(mean_score)
  }
}
```

```{r}
anime_data <- anime %>%
  mutate(genres_score = map_dbl(genres, ~ category_mean_score(.x, genres_mean_scores)),
         themes_score = map_dbl(themes, ~ category_mean_score(.x, themes_mean_scores)),
         studios_score = map_dbl(studios, ~ category_mean_score(.x, studios_mean_scores)),
         demographics_score = map_dbl(demographics, ~ category_mean_score(.x, demographics_mean_scores)),
         producers_score = map_dbl(producers, ~ category_mean_score(.x, producers_mean_scores))) %>%
  select(-c(genres, themes, studios, demographics, producers, title)) %>%
  mutate_if(is.character, factor)

save(anime_data, file = "data/anime_data.RData")
```

# Models

```{r, message=FALSE}
library(tidymodels)
load("data/anime_data.RData")
tidymodels_prefer()

set.seed(1)
anime_split <- initial_split(anime_data, strata = "score")
anime_train <- training(anime_split)
anime_test <- testing(anime_split)
```

Consider creating a [custom step](https://www.tidymodels.org/learn/develop/recipes/#create-the-prep-method) for the recipe.

## Linear Model

```{r}
anime_recipe <- recipe(score ~ ., data = anime_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_scale(all_numeric_predictors())

set.seed(1)
anime_folds <- vfold_cv(anime_train, v = 5)
```

```{r}
lm_model <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

lm_workflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(anime_recipe)

lm_fit <- lm_workflow %>%
  fit(anime_train)

augment(lm_fit, new_data = anime_test) %>% 
  mutate(avg_error = .pred - score) %>% 
  ggplot(aes(x = avg_error)) +
  geom_histogram()

augment(lm_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red")

augment(lm_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

save(lm_fit, file = "models/lm_fit.rda")
```

```{r}
library(corrplot)
anime_train %>%
  select_if(is.numeric) %>%
  cor()
```

Nearest Neighbor

```{r}
knn_model <- nearest_neighbor(neighbors = tune()) %>%
  set_mode("regression") %>%
  set_engine("kknn")

knn_workflow <- workflow() %>%
  add_model(knn_model) %>%
  add_recipe(anime_recipe)

neighbors_grid <- grid_regular(neighbors(range = c(10, 100)),
                               levels = 10)

tune_res <- tune_grid(knn_workflow,
                      resamples = anime_folds,
                      grid = neighbors_grid)

autoplot(tune_res)
```

```{r}
best_neighbors <- select_best(tune_res, metric = "rmse")

knn_final <- finalize_workflow(knn_workflow, best_neighbors)

knn_final_fit <- knn_final %>% 
  fit(anime_train)

augment(knn_final_fit, new_data = anime_test) %>% 
  mutate(avg_error = .pred - score) %>% 
  ggplot(aes(x = avg_error)) +
  geom_histogram()

augment(knn_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red")

augment(knn_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

save(knn_final_fit, file = "models/knn_fit.rda")
```

Boosted Model (doesn't work)

```{r}
# https://juliasilge.com/blog/xgboost-tune-volleyball/
boost_model <- boost_tree(min_n = tune(),
                          mtry = tune(),
                          learn_rate = tune(),
                          tree_depth = tune(),
                          sample_size = tune(),
                          loss_reduction = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

boost_workflow <- workflow() %>%
  add_model(boost_model) %>%
  add_recipe(anime_recipe)

# cover hyperspace as much as possible
boost_grid <- grid_latin_hypercube(min_n(),
                                   finalize(mtry(), anime_train),
                                   learn_rate(),
                                   tree_depth(),
                                   sample_size = sample_prop(),
                                   loss_reduction(),
                                   size = 50)

tune_res <- tune_grid(boost_workflow,
                      resamples = anime_folds,
                      grid = boost_grid)

autoplot(tune_res, metric = "rmse")
```

```{r}
best_params <- select_best(tune_res, "rmse")

final_boost <- finalize_workflow(boost_workflow, best_params)

final_boost_fit <- final_boost %>% 
  fit(anime_train)

augment(final_boost_fit, new_data = anime_test) %>% 
  mutate(avg_error = .pred - score) %>% 
  ggplot(aes(x = avg_error)) +
  geom_histogram()

augment(final_boost_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red")

augment(final_boost_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

# not predicting above a certain point
predict(final_boost_fit, new_data = anime_test) %>% 
  pull(.pred) %>% 
  summary()
```

Random Forest

```{r}
rf_model <- rand_forest() %>%
  set_mode("regression") %>%
  set_engine("ranger")

rf_workflow <- workflow() %>%
  add_model(rf_model) %>%
  add_recipe(anime_recipe)

rf_fit <- rf_workflow %>%
  fit(anime_train)

augment(rf_fit, anime_test) %>%
  mutate(avg_error = .pred - score) %>% 
  ggplot(aes(x = avg_error)) +
  geom_histogram()

# spy family
predict(rf_fit,
        new_data = tibble(type = "tv",
                       episodes = 13,
                       source = "manga",
                       members = 588168,
                       favorites = 5559,
                       rating = "pg_13",
                       genres_score = 6.718383,
                       themes_score = 7.608718,
                       studios_score = 7.256266,
                       demographics_score = 7.07873,
                       producers_score = 7.254288))

# chainsaw man
predict(rf_fit,
        new_data = tibble(type = "tv",
                       episodes = 12,
                       source = "manga",
                       members = 966715,
                       favorites = 31151,
                       rating = "r",
                       genres_score = category_mean_score("['Action', 'Fantasy']", genres_mean_scores),
                       themes_score = category_mean_score("['Gore']", themes_mean_scores),
                       studios_score = category_mean_score("['MAPPA']", studios_mean_scores),
                       demographics_score = category_mean_score("['Shounen']", demographics_mean_scores),
                       producers_score = category_mean_score("['Other or NA']", producers_mean_scores)))

# suzume
predict(rf_fit,
        new_data = tibble(type = "movie",
                       episodes = 1,
                       source = "original",
                       members = 108909,
                       favorites = 1006,
                       rating = "pg_13",
                       genres_score = category_mean_score("['Fantasy']", genres_mean_scores),
                       themes_score = category_mean_score("['Other or NA']", themes_mean_scores),
                       studios_score = category_mean_score("['CoMix Wave Films']", studios_mean_scores),
                       demographics_score = category_mean_score("[]", demographics_mean_scores),
                       producers_score = category_mean_score("['STORY']", producers_mean_scores)))
```

```{r}
set.seed(1)
small_train <- anime_train[1:500, ]
anime_folds <- vfold_cv(small_train)

rf_spec_new <- rand_forest(mtry = tune(),
                           trees = 1000) %>%
  set_engine("ranger") %>%
  set_mode("regression")

rf_rec <- recipe(score ~ ., data = small_train)

rf_workflow <- workflow() %>%
  add_recipe(rf_rec) %>%
  add_model(rf_spec_new)

param_grid <- grid_regular(mtry(range = c(2, 5)),
                           levels = 4)

tune_res <- tune_grid(rf_workflow,
                      resamples = anime_folds,
                      grid = param_grid)

autoplot(tune_res)
```

```{r}
best <- select_best(tune_res)
rf_final <- finalize_workflow(rf_workflow, best)

rf_final_fit <- rf_final %>% fit(small_train)

augment(rf_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)
```

- Random forest

Test PC regression

```{r}
# specify recipe
pca_recipe <- recipe(score ~ ., data = anime_train) %>%
  step_novel(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors()) %>%
  step_normalize(all_predictors()) %>%
  step_pca(all_predictors(), threshold = tune())

# create workflow object
pca_workflow <- workflow() %>%
  add_recipe(pca_recipe) %>%
  add_model(lm_model)

# threshold values to try
threshold_grid <- grid_regular(threshold(), levels = 10)

# fit model for each threshold
tune_res <- tune_grid(object = pca_workflow,
                      resamples = anime_folds,
                      grid = threshold_grid)

# plot metrics
autoplot(tune_res)
```

```{r}
# select the best model based on the given metric
best_threshold <- select_best(tune_res, metric = "rmse")

# refit using the whole training data set
pca_final <- finalize_workflow(pca_workflow, best_threshold)
pca_final_fit <- fit(pca_final, data = anime_train)

augment(pca_final_fit, new_data = anime_test) %>% 
  mutate(avg_error = .pred - score) %>% 
  ggplot(aes(x = avg_error)) +
  geom_histogram()

augment(pca_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red")

augment(pca_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)
```

```{r}
# chainsaw man
predict(pca_final_fit,
        new_data = tibble(type = "tv",
                       episodes = 12,
                       source = "manga",
                       members = 966715,
                       favorites = 31151,
                       rating = "r",
                       genres_score = category_mean_score("['Action', 'Fantasy']", genres_mean_scores),
                       themes_score = category_mean_score("['Gore']", themes_mean_scores),
                       studios_score = category_mean_score("['MAPPA']", studios_mean_scores),
                       demographics_score = category_mean_score("['Shounen']", demographics_mean_scores),
                       producers_score = category_mean_score("['Other or NA']", producers_mean_scores)))

# spy family
predict(lm_fit,
        new_data = tibble(type = "tv",
                       episodes = 13,
                       source = "manga",
                       members = 588168,
                       favorites = 5559,
                       rating = "pg_13",
                       genres_score = 6.718383,
                       themes_score = 7.608718,
                       studios_score = 7.256266,
                       demographics_score = 7.07873,
                       producers_score = 7.254288))
```


