---
title: "Predicting Anime Scores"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)
```

# Prerequisites

```{r, message=FALSE}
# load libraries
library(tidyverse)
library(tidymodels)
library(patchwork)
library(ggrepel)
library(vip)

# set theme for plots
theme_set(theme_bw())

# load data
anime_raw <- read_csv("data/anime.csv")
```


# Data cleaning {.tabset}

Variable | Description
:--|:--
`title` | Anime title
`score` | [Weighted score](https://myanimelist.net/info.php?go=topanime) on MyAnimeList (out of 10)
`type` | Anime type (e.g., TV, movie, OVA)
`source` | Source that the anime was adapted from (e.g, manga, light novel, original)
`members` | Number of members who added the anime to their list
`favorites` | Number of members who favorited the anime in their list
`rating` | Age rating (e.g., PG, PG-13, R)
`genres` | Genre(s) (e.g., Action, Drama, Comedy)
`themes` | Theme(s) (e.g., Isekai, Historical, Music)
`demographics` | Primary audience (e.g., shounen, shoujo, seinen - more details [here](https://www.cbr.com/four-main-shonen-shojo-seinen-josei-manga-demographics-explained/))
`studios` | Studio(s) that animate the anime
`producers` | Producer(s) that fund the anime

```{r}
anime <- anime_raw %>%
  # filter out any animes that do not have scores
  drop_na(score) %>%
  # keep only animes that have finished airing (since scores can change while it's airing)
  filter(status == "finished_airing") %>%
  # select relevant variables
  select(title, score, type, source, members, favorites, rating, 
         genres, themes, demographics, studios, producers) %>%
  # filter out rows that have NA values
  drop_na()

anime
```

Multi-label issue
- Computationally expensive
- Want less parameters

```{r}
# fills in empty strings in a vector
replace_empty_string <- function(.str) {
  ifelse(.str == "", "Other or NA", .str)
}

# returns a dataframe with the mean score of each unique value in a given category
get_mean_scores <- function(df, category) {
  mean_scores <- df %>%
    # remove square brackets
    mutate(cleaned_category = str_remove(!!sym(category), "\\["),
           cleaned_category = str_remove(cleaned_category, "\\]")) %>%
    # separate column into multiple rows for each unique value in the category column
    separate_rows(cleaned_category, sep = ",") %>% 
    # remove apostrophes and whitespace
    mutate(cleaned_category = str_remove(cleaned_category, "\\'"),
           cleaned_category = str_remove(cleaned_category, "\\'"),
           cleaned_category = str_trim(cleaned_category)) %>%
    # replace missing values with filler
    mutate_at("cleaned_category", ~ replace_empty_string(.x)) %>%
    # get mean score for each category
    group_by(cleaned_category) %>%
    summarise(score = mean(score)) %>%
    # sort from highest to lowest
    arrange(desc(score))
  
  # save dataframe as CSV file
  file_name <- str_glue("data/mean_scores_{category}.csv")
  write_csv(mean_scores, file_name)
  
  # return dataframe
  return(mean_scores)
}
```

## Genres

```{r}
get_mean_scores(anime, "genres")
```

## Themes

```{r}
get_mean_scores(anime, "themes")
```

## Studios

```{r}
get_mean_scores(anime, "studios")
```

## Demographics

```{r}
get_mean_scores(anime, "demographics")
```

## Producers

```{r}
get_mean_scores(anime, "producers")
```

## Calculate scores

```{r, message=FALSE}
# calculate overall median score
total_mean_score <- anime %>% 
  pull(score) %>% 
  median()

# example: maps something like categories = ['category1', 'category2'] to a mean score
category_mean_score <- function(categories, df_map, replace_empty = total_mean_score) {
  # get mapped values
  category <- df_map %>% pull(1)
  score <- df_map %>% pull(2)
  
  # use overall median score if input is empty
  if (categories == "[]") {
    return(replace_empty)
  }
  
  # otherwise, calculate the mean score over those categories
  else {
    mean_score <- categories %>%
      # remove brackets and single quotes
      str_remove("\\[") %>%
      str_remove("\\]") %>%
      str_remove_all("\\'") %>%
      # split at commas
      strsplit(split = ", ") %>%
      unlist() %>%
      # map each category to a score and calculate the mean
      plyr::mapvalues(from = category, 
                      to = score,
                      warn_missing = FALSE) %>%
      as.numeric() %>%
      mean()
    
    return(mean_score)
  }
}

# load dataframes with mean scores 
mean_scores_genres <- read_csv("data/mean_scores_genres.csv")
mean_scores_themes <- read_csv("data/mean_scores_themes.csv")
mean_scores_studios <- read_csv("data/mean_scores_studios.csv")
mean_scores_demographics <- read_csv("data/mean_scores_demographics.csv")
mean_scores_producers <- read_csv("data/mean_scores_producers.csv")

anime_clean <- anime %>%
  # get mean scores for multi-label columns
  mutate(genres_score = map_dbl(genres, ~ category_mean_score(.x, mean_scores_genres)),
         themes_score = map_dbl(themes, ~ category_mean_score(.x, mean_scores_themes)),
         studios_score = map_dbl(studios, ~ category_mean_score(.x, mean_scores_studios)),
         demographics_score = map_dbl(demographics, ~ category_mean_score(.x, mean_scores_demographics)),
         producers_score = map_dbl(producers, ~ category_mean_score(.x, mean_scores_producers))) %>%
  # remove old columns
  select(-c(genres, themes, studios, demographics, producers)) %>%
  # convert character columns into factors
  mutate_if(is.character, factor)

# save as CSV file
write_csv(anime_clean, "data/anime_clean.csv")
```

# Exploratory data analysis {.tabset}

```{r}
# load cleaned data
anime_clean <- read_csv("data/anime_clean.csv")
anime_clean
```

## MAL scores

```{r}
# histogram
p1 <- anime_clean %>%
  ggplot(aes(x = score)) +
  geom_histogram(bins = 50) +
  labs(title = "Histogram of MAL scores")

# boxplot
p2 <- anime_clean %>%
  ggplot(aes(x = score)) +
  geom_boxplot() +
  labs(title = "Boxplot of MAL scores")

# combine plots
p1 + p2 + plot_layout(ncol = 1)
```

```{r}
# correlation plot for numeric variables
anime_clean %>%
  select_if(is.numeric) %>%
  cor() %>%
  corrplot::corrplot(method = "number")
```

## Type

```{r}
anime_clean %>%
  # boxplots by type, ordered by median score
  ggplot(aes(x = reorder(type, score, FUN = median), 
             y = score, 
             color = reorder(type, score, FUN = median))) +
  geom_boxplot() +
  # horizontal dashed line for overall mean score
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  # update labels and other plot features
  labs(title = "MAL scores by type",
       x = "Genre",
       y = "Score",
       color = "Genre") +
  theme(legend.position = "none")
```

## Source

```{r}
anime_clean %>%
  # boxplot by source, ordered by median score
  ggplot(aes(x = reorder(source, score, FUN = median), 
             y = score, 
             color = reorder(source, score, FUN = median))) +
  geom_boxplot() +
  # horizontal dashed line for overall mean score
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  # update labels and other plot features
  labs(title = "MAL scores by source",
       x = "Source",
       y = "Score",
       color = "Source") +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")
```

## Members

```{r}
anime_clean %>%
  # scatter plot
  ggplot(aes(x = members, y = score)) +
  geom_point() +
  # horizontal dashed line for overall mean score
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  # point labels for titles with the most members
  geom_text_repel(data = subset(anime_clean, members > 2.5e6),
                  aes(label = title),
                  box.padding = 0.6) +
  # update labels
  labs(title = "MAL scores vs. number of members",
       x = "Number of members",
       y = "Score")
```

## Favorites

```{r}
anime_clean %>%
  # scatter plot
  ggplot(aes(x = favorites, y = score)) +
  geom_point() +
  # horizontal dashed line for overall mean score
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  # point labels for titles with the most favorites
  geom_text_repel(data = subset(anime_clean, favorites > 1.5e5),
                  aes(label = title),
                  box.padding = 1.1) +
  # update labels
  labs(title = "MAL scores vs. number of favorites",
       x = "Number of favorites",
       y = "Score")
```

## Rating

```{r}
anime_clean %>%
  # boxplot by rating, ordered by median score
  ggplot(aes(x = reorder(rating, score, FUN = median), 
             y = score, 
             color = reorder(rating, score, FUN = median))) +
  geom_boxplot() +
  # horizontal dashed line for overall mean score
  geom_hline(aes(yintercept = mean(score)),
             linetype = "dashed") +
  # update labels and other plot features
  labs(title = "MAL Scores by rating",
       x = "Genre",
       y = "Score",
       color = "Genre") +
  theme(axis.title.x = element_blank(),
        legend.position = "none")
```

## Derived mean scores

```{r, message=FALSE}
anime_clean %>%
  # convert to wide format
  select(contains("score")) %>%
  pivot_longer(cols = contains("_score"),
               names_to = "type",
               values_to = "type_score") %>%
  # scatter plot + smoothing
  ggplot(aes(x = type_score, y = score)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ type, nrow = 2) +
  # update labels
  labs(title = "MAL scores vs. derived mean scores",
       x = "Derived mean score",
       y = "MAL score")
```

# Models

## Preparing the data

```{r, message=FALSE}
# load cleaned data
anime_clean <- read_csv("data/anime_clean.csv")

# partition training and testing sets
set.seed(1)
anime_split <- initial_split(anime_clean, strata = "score")
anime_train <- training(anime_split)
anime_test <- testing(anime_split)

# create 5-fold cross-validation object
anime_folds <- vfold_cv(anime_train, v = 5)

# specify recipe
anime_recipe <- recipe(score ~ ., data = anime_train) %>%
  step_rm(title) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_scale(all_numeric_predictors())
```

## Linear regression

```{r}
# specify linear regression model
lm_model <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

# specify workflow
lm_workflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(anime_recipe)

# fit model using cross-validation
lm_fit <- lm_workflow %>%
  fit_resamples(anime_folds)

# select the best model and fit
lm_final_fit <- lm_fit %>%
  select_best("rmse") %>%
  finalize_workflow(lm_workflow, .) %>%
  fit(anime_train)

# plot actual vs. predicted scores
augment(lm_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 10)) +
  labs(title = "Linear model: actual vs. predicted scores",
       x = "Predicted score",
       y = "Actual score")

# calculate RMSE
augment(lm_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

# save final model
save(lm_final_fit, file = "models/lm_fit.rda")

# get coefficient estimates
lm_final_fit %>%
  tidy() %>%
  mutate(significant = ifelse(p.value < 0.05, "yes", "no"))
```

## Nearest Neighbor

```{r}
# specify KNN model
knn_model <- nearest_neighbor(neighbors = tune()) %>%
  set_mode("regression") %>%
  set_engine("kknn")

# specify workflow
knn_workflow <- workflow() %>%
  add_model(knn_model) %>%
  add_recipe(anime_recipe)

# specify hyperparameters
neighbors_grid <- grid_regular(neighbors(range = c(5, 50)),
                               levels = 10)

# fit model using cross-validation and hyperparameters
knn_tune_res <- tune_grid(knn_workflow,
                          resamples = anime_folds,
                          grid = neighbors_grid)

# plot results
autoplot(knn_tune_res)

# select the best model and fit
knn_final_fit <- knn_tune_res %>%
  select_best("rmse") %>%
  finalize_workflow(knn_workflow, .) %>%
  fit(anime_train)

# plot actual vs. predicted scores
augment(knn_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 10)) +
  labs(title = "KNN model: actual vs. predicted scores",
       x = "Predicted score",
       y = "Actual score")

# calculate RMSE
augment(knn_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

# save final model
save(knn_tune_res, file = "models/knn_tune_res.rda")
save(knn_final_fit, file = "models/knn_fit.rda")
```

## Boosted trees

https://juliasilge.com/blog/xgboost-tune-volleyball/

```{r}
# specify boosted trees model
boost_model <- boost_tree(trees = 1000,
                          min_n = tune(),
                          mtry = tune(),
                          learn_rate = tune(),
                          tree_depth = tune(),
                          sample_size = tune(),
                          loss_reduction = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

# specify workflow
boost_workflow <- workflow() %>%
  add_model(boost_model) %>%
  add_recipe(anime_recipe)

# specify hyperparameters (cover hyperparameter space as much as possible)
boost_grid <- grid_latin_hypercube(min_n(),
                                   finalize(mtry(), anime_train),
                                   learn_rate(),
                                   tree_depth(),
                                   sample_size = sample_prop(),
                                   loss_reduction(),
                                   size = 50)

# fit model using cross-validation and hyperparameters
boost_tune_res <- tune_grid(boost_workflow,
                            resamples = anime_folds,
                            grid = boost_grid)

# plot results
autoplot(boost_tune_res, metric = "rmse")

# select the best model and fit
boost_final_fit <- boost_tune_res %>%
  select_best("rmse") %>%
  finalize_workflow(boost_workflow, .) %>%
  fit(anime_train)

# plot actual vs. predicted scores
augment(boost_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 10)) +
  labs(title = "Boosted trees: actual vs. predicted scores",
       x = "Predicted score",
       y = "Actual score")

# calculate RMSE
augment(boost_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

# variable importance plot
boost_final_fit %>%
  extract_fit_parsnip() %>%
  vip() + 
  labs(title = "Boosted trees: variable importance",
       x = "Predictors",
       y = "Importance")

# save final model
save(boost_tune_res, file = "models/boost_tune_res.rda")
save(boost_final_fit, file = "models/boost_fit.rda")
```

## Random forest

```{r}
# specify random forest model
rf_model <- rand_forest(mtry = tune(),
                        trees = 1000,
                        min_n = tune()) %>%
  set_mode("regression") %>%
  set_engine("ranger", importance = "impurity")

# specify workflow
rf_workflow <- workflow() %>%
  add_model(rf_model) %>%
  add_recipe(anime_recipe)

# specify hyperparameters
rf_tune_res <- tune_grid(rf_workflow,
                         resamples = anime_folds,
                         grid = 30)

# plot results
autoplot(rf_tune_res, metric = "rmse")

# select the best model and fit
rf_final_fit <- rf_tune_res %>%
  select_best("rmse") %>%
  finalize_workflow(rf_workflow, .) %>%
  fit(anime_train)

# plot actual vs. predicted scores
augment(rf_final_fit, new_data = anime_test) %>% 
  ggplot(aes(x = .pred, y = score)) +
  geom_point(alpha = 0.4) +
  geom_abline(lty = 2, color = "red") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 10)) +
  labs(title = "Random forest: actual vs. predicted scores",
       x = "Predicted score",
       y = "Actual score")

# calculate RMSE
augment(rf_final_fit, new_data = anime_test) %>%
  rmse(truth = score, estimate = .pred)

# variable importance plot
rf_final_fit %>%
  extract_fit_parsnip() %>%
  vip() + 
  labs(title = "Random forest: variable importance",
       x = "Predictors",
       y = "Importance")

# save final model
save(rf_tune_res, file = "models/rf_tune_res.rda")
save(rf_final_fit, file = "models/rf_fit.rda")
```
